\dz{Unsorted literature list:}


Practical results of the thesis are:
eased tuning of neurons, configuring populations, achieving EI balance (tight?), enabling first RelNets, deployement of delay (synfire) chains, 


Neuromorphic systems challenges:~\cite{Indiveri_etal15, Indiveri_Liu15}\\
Homeostatic plasticity:~\cite{Turrigiano_Nelson04}\\
sWTA by Giacomo, Elizabetta and Rodney. But also Neuromorphic cognition! definition of neuromorphic agents (active vs reactive):~\cite{Indiveri_etal09}. The meaning and significance are extrinsic to the computation in traditional computing. Motivation for Rel-Nets as steps towards neuromorphic cognition. Belief propagation, factor graphs\\
\dz{If cortex is not just an inference machine}\\
Spiking belief propagation network with LSM readouts:~\cite{Steimer_etal09}\\
Simulation tools review and strategies:~\cite{Brette_etal07}\\
BrainScales reference:~\cite{Pehle_etal22}\\
Spike timing synchronization in cortical function: \cite{Riehle_etal97}\\
For the delay chains to motivate inhibition:~\cite{Moradi04} (Information coding and oscillatory activity in synfire neural networks with and without inhibitory coupling). Are synfire chains Markov processes?\\
R-STDP implementation for Spinnaker:~\cite{Shahsavari_etal21}.\\
Combination of TTFS and R-STDP, TTFS serves is a WTA to enable STDP change: \cite{Mozafari_etal18}
Bidirectional BMI using ROLLS:~\cite{Boi_etal16}\\
Palimpsest memories stored in memristive synapses: \cite{Giotis_etal22}\\
Caviar paper:~\cite{Serrano-Gotarredona_etal09}\\
Charlotte, the importance of biological design motivation, also lack of spiking benchmarking etc:\cite{Frenkel_etal23}\\
Panzeri, noise correlations in populations codes:~\cite{Panzeri_etal22}\\
Bellec paper about e-prop, it's important to motivate locality of the learning, and how it's energy efficient. Training on hardware saves on data transmission.~\cite{Bellec_etal20}\\
Basics of RL approach from Christiano: \dz{ADD}\\
SSA, anomaly detection with SFA in the neurons, Nick Denler: \cite{Dennler_etal21a}\\
Train online and deploy approach for SNNs by Ugurcan for D2: \cite{Cakal_etal24}, \dz{our paper with Julian~\cite{Beuchel_etal21}}\\
perched flight references for RL applications \dz{Find, Add}\\
HFO detection on DYNAP-SE, Mohammad, Karla, Filippo~\cite{Sharifshazileh_etal21}\\
Charlotte: Which data domains do we work with. Everything temporal makes sense SNNs (as for steady state we need to inevitably integrate events and lose precision). EEG, EMG, Heart monitors and other anomaly search data streams \\
Thermal changes in the circuits: \cite{}\\
Parameter tuning: \cite{Neftci_Indiveri10, Gao_etal12}\\
OPTICAL NETWORKS, ESMs with nanotubes and other things: \dz{ADD REFS}\\
State dependednt compuatation Emre: \cite{Neftci_etal10}
A \ac{MOSFET} transistor~\cite{Colinge2002}\\

ON CHIP UNSUPERVISED LEARNING WITH WTA  \cite{Kreiser_etal18a}


\dz{The following is taken from~\cite{Zendrikov_etal23} and requires thorough adaptation from the paper format to thesis.}